Open Science, Open Plant Pathology

### 2019-02-15 analysis/paper/paper.Rmd
Update citation for Gold Book

In order for us to easily discuss the topic, we first must define what we mean so that we may clearly communicate. Many of the terms used in this area have varying definitions that may or may not agree with each other. For instance, reproducible research is recently hightlighted by many authors [@Baker2016a; @Iqbal2016; @Nature2016; @Weissgerber2016; @Brunsdon2015; @Sweedler2015; @Fitzjohn2014; @Ioannidis2014; @Fidler2013; @Stodden2013] as an important issue. This has resulted in attepmts to define "reproducibility", _e.g._ [@Patil2016], therefore the following definitions will be used for these terms throughout this paper.

@@

The International Union of Pure and Applied Chemistry defines repeatability in the "Compendium of Chemical Terminology Gold Book" [@mcnaughtcompendium],

> "The closeness of agreement between independent results obtained with the same method on identical test material, under the same conditions (same operator, same apparatus, same laboratory and after short intervals of time). The measure of repeatability is the standard deviation qualified with the term: `repeatability' as repeatability standard deviation. In some contexts repeatability may be defined as the value below which the absolute difference between two single test results obtained under the above conditions, may be expected to lie with a specified probability."

@@

The International Union of Pure and Applied Chemistry defines reproducibility in the "Compendium of Chemical Terminology Gold Book" [@mcnaughtcompendium],

>"The closeness of agreement between independent results obtained with the same method on identical test material but under different conditions (different operators, different apparatus, different laboratories and/or after different intervals of time). The measure of reproducibility is the standard deviation qualified with the term 'reproducibility' as reproducibility standard deviation. In some contexts reproducibility may be defined as the value below which the absolute difference between two single test results on identical material obtained under the above conditions, may be expected to lie with a specified probability. Note that a complete statement of reproducibility requires specification of the experimental conditions which differ."

>>>>

In order for us to easily discuss the topic, we first must define what we mean so that we may clearly communicate. Many of the terms used in this area have varying definitions that may or may not agree with each other. For instance, reproducible research is recently hightlighted by many authors [@Baker2016a; @Iqbal2016; @Nature2016; @Weissgerber2016; @Brunsdon2015; @Sweedler2015; @Fitzjohn2014; @Ioannidis2014; @Fidler2013; @Stodden2013] as an important issue. This has resulted in attepmts to define "reproducibility", _e.g._ Patil
_et al._ [-@Patil2016], therefore the following definitions will be used for these terms throughout this paper.

@@

The International Union of Pure and Applied Chemistry defines repeatability in the "Compendium of Chemical Terminology -- Gold Book" as,

> "The closeness of agreement between independent results obtained with the same method on identical test material, under the same conditions (same operator, same apparatus, same laboratory and after short intervals of time). The measure of repeatability is the standard deviation qualified with the term: `repeatability' as repeatability standard deviation. In some contexts repeatability may be defined as the value below which the absolute difference between two single test results obtained under the above conditions, may be expected to lie with a specified probability", [@mcnaught1997compendium].

@@

The International Union of Pure and Applied Chemistry defines reproducibility in the "Compendium of Chemical Terminology -- Gold Book" as,

>"The closeness of agreement between independent results obtained with the same method on identical test material but under different conditions (different operators, different apparatus, different laboratories and/or after different intervals of time). The measure of reproducibility is the standard deviation qualified with the term 'reproducibility' as reproducibility standard deviation. In some contexts reproducibility may be defined as the value below which the absolute difference between two single test results on identical material obtained under the above conditions, may be expected to lie with a specified probability. Note that a complete statement of reproducibility requires specification of the experimental conditions which differ", [@mcnaught1997compendium].
